Interpolation for Modeling and Predicting Variability

### 2019-05-03 Disseration/prelim.tex
Updated abstract to be more clear.

% The abstract is required and should be <=250 words for thesis, <=350 words for dissertation.
\abstract{Approximation is an important problem. This work presents applications of interpolants to modeling random variables. Specifically, this work studies the prediction of distributions of random variables applied to computer system throughput variability. New methods for interpolating data with many dimensions are presented and novel theoretical error bounds are constructed for piecewise linear interpolation. Finally, a mathematical software for approximating distributions from data samples via monotone quintic splines is proposed.}

>>>>

% The abstract is required and should be <=250 words for thesis, <=350 words for dissertation.
\abstract{Function approximation is an important problem. This work presents applications of interpolants to modeling random variables. Specifically, this work studies the prediction of distributions of random variables applied to computer system throughput variability. New methods for interpolating data with moderately high dimension are presented and novel theoretical error bounds are constructed for piecewise linear interpolation. Finally, a mathematical software for approximating distributions from data samples via monotone quintic splines is proposed.}
